Big Ideas in Sports Analytics and Statistical Tools for their Investigation

### 2023-01-10 response_to_reviewers_R1.Rmd

---
title: "Response to Reviewers"
date: "2023-01-03"
output:
  pdf_document: default
  html_document: default
---

@@

Overall, the paper is now much more comprehensive, complete, and clear; I think it
will serve as a very useful introduction to the field of sports analytics. I have only a few
suggestions and points of confusion to share, which I hope the authors will examine before
submitting the final version. They are all fairly minor.

> Thank you for your feedback.

- If there is still space allowed in the abstract, I think you could consider explicitly
mentioning the three big ideas (expected value of a game state, win probability, and
measures of team strength). This would give readers a better idea of what is to come
and also allow people to find your article more easily if they are interested in one of
those specific topics.

> Thank you for this suggestion. We have added the three (now four) big ideas explicitly to the abstract.

@@

> We have clarified this language. It now reads: "Lopez (2020) also concludes that coaches are too conservative on 4th down decision making, but notes further that past estimates of the magnitude of how conservative coaches are on 4th down may be overstated due to the way in which to go yardage was recorded only approximately in the past."

- In Section 2.3, you write “NHL coaches do not always employ the optimal strategies”,
but it isn’t clear what those strategies are in reference to the previous discussion. Is
pulling the goalie optimal?

> We have added a clarification that coaches usually wait too long to pull their goalies.

- In the second formula of Section 4.1, the right hand side of the equation has a 2, but
it should be an $\alpha$.

@@

This revised version is a significant improvement over the previous version and the reviewers have addressed my major concerns with the paper with one exception.

Suggested Changes:

- The authors have now made clearer the limitation in scope of this manuscript related to player evaluation. Perhaps, a statement regarding this can be added to the abstract.

> We have a statement to this effect to the abstract. It now reads: "We also describe opportunities to share analytical work, but
omit an in-depth discussion of individual player evaluation as beyond our scope."

### 2023-01-10 sports_analytics.Rmd
source figure

```{r epv-demo, out.width="100%", fig.cap="Player locations and estimated EPV for a possession during the Miami Heat (red) vs. Brooklyn Nets (black) NBA game on November 1, 2013. The captured moment is when Miami's Mario Chalmers just releases a three-point shot, which ends up as a missed field goal."}
# Source: https://github.com/dcervone/EPVDemo/blob/master/gifs/poss_12.gif
# library(magick)
# epv <- image_read("https://github.com/dcervone/EPVDemo/blob/master/gifs/poss_12.gif?raw=true")
# image_write(epv[529], "epv_snap.png")
knitr::include_graphics("epv_snap.png")
```

>>>>

```{r epv-demo, out.width="100%", fig.cap="Player locations and estimated EPV for a possession during the Miami Heat (red) vs. Brooklyn Nets (black) NBA game on November 1, 2013. The captured moment is when Miami's Mario Chalmers just releases a three-point shot, which ends up as a missed field goal. Figure created by Cervone, et al. \\url{https://github.com/dcervone/EPVDemo}"}
# Source: https://github.com/dcervone/EPVDemo/blob/master/gifs/poss_12.gif
# library(magick)
# epv <- image_read("https://github.com/dcervone/EPVDemo/blob/master/gifs/poss_12.gif?raw=true")
# image_write(epv[529], "epv_snap.png")
knitr::include_graphics("epv_snap.png")
```
